\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-09 ms.tex
stddev

We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
\changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (revised) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}
We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.

>>>>

We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
\changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values and standard deviations of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (revised) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}
We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.
